---
title: "Gov 50 Final Project"
author: Zoe Hopkins
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

My proposed project will use afrobarometer look at the correlation between military and police presence and outlook on the state of respondent's the country, and their outlook on their own condition. I will compare the UN's five geographical regions: North, East, West, Middle and Southern Africa. I am interested in how this question varies by region: i.e. which region thinks of itself as headed in "the best" direction, and how police and military presence plays into this. My hypothesis is that the regions with the most police and military presence think that they are headed in worse directions, given that heightened military presence often suggests the presence of conflict. 

## Data Visualization 
```{r}
library(tidyverse)

```

```{r}
library(ggplot2)
load("afrobarometer2016.RData")
```

```{r}
afro|>
  ggplot(mapping=aes(x=COUNTRY.BY.REGION))+
  geom_histogram()
```
test
